---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# triangles

<!-- badges: start -->
<!-- badges: end -->

Wrap C code to calculate Pythagorean triples.

## Installation

You can install the development version of triangles with

``` r
# install.packages("remotes")
remotes::install_github("jonocarroll/triangles")
```

## Example

This package is purely for demonstration purposes, supporting this blog post: https://jcarroll.com.au/TBA

The wrapped C code involves many features I learned about so I built this package 
to support the blog post in an effort to capture as many as possible. The processes 
here are not new at all, but I found many of the existing resources to be either 
out of date or confusing.

The function `triangles()` takes a maximum hypotenuse length `maxval` and produces 
a `data.frame()` in R. The columns represent the lengths of the sides of a 
right triangle `a`, `b`, and `c` such that all of these are integers, along with the 
sum of these (the perimeter of the triangle)

```{r}
library(triangles)

triangles(20)
```

This is a complete `data.frame` returned from C

```{r}
x <- triangles(20)
str(x)
x[x$sum > 20 & x$sum < 35, ]
```

Various iterations of the C code can be found in [inst/src](inst/src).
